---
title: "Quality Control on BALK culture data"
author: "Katherine Heal"
date: "May 22, 2019"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(dev = 'pdf')
library(tidyverse)
```

#Set your datafiles
```{r, error = FALSE, warning=FALSE, message=FALSE}
#Read in your output from Skyline
Datfile1 <- "./datafiles/HILICPos_DiatomBatch1_SkylineExport.csv"

#Read in a csv that has which samples go to which blanks
BlankMatcherFile <- "./datafiles/Samps_with_Blanks.csv"

#Set your flag to find standards to base RT off of
StdFlag <- c("170410_Smp_KM1513-15m_A", "180702_Smp_S7E41D30_1")

#Set your parameters
SNmin = 3
ppmflex = 6
Areamin = 20000

RTflex = 2
BlankRatiomax = 5
```

Read in data, flags for Signal:Noise, ppm, minimum area.
Next, flag for Retention Time being off of standards
```{r, error = FALSE, warning=FALSE, message=FALSE}
#Says which are blanks and which are samples
BlankMatcher <- read_csv(BlankMatcherFile)

#First do easy flags - SN, ppm, Areamin
Datorig <- read.csv(Datfile1) %>%
  select(-Protein.Name, -Protein) %>%
  mutate(Retention.Time = as.numeric(as.character(Retention.Time))) %>%
  mutate(Area = as.numeric(as.character(Area))) %>%
  mutate(Background = as.numeric(as.character(Background))) %>%
  mutate(Mass.Error.PPM = as.numeric(as.character(Mass.Error.PPM))) 

Dat1 <- Datorig %>%
  filter(Replicate.Name %in% BlankMatcher$Replicate.Name) %>%
  mutate(SNFlag = ifelse((Area/Background < SNmin), "SNFlag", NA)) %>%
  mutate(ppmFlag = ifelse((Mass.Error.PPM > ppmflex), "ppmFlag", NA)) %>%
  mutate(areaminFlag = ifelse((Area < Areamin), "areaminFlag", NA))

#Next do RT flag compared to standard or a template
RT_of_Stds <- Datorig %>%
  filter(Replicate.Name %in% StdFlag) %>%
  select(Precursor.Ion.Name, Retention.Time) %>%
  group_by(Precursor.Ion.Name) %>%
  summarise(RT_ref = mean((Retention.Time), na.rm = TRUE))

Dat2 <- Dat1 %>%
  left_join(RT_of_Stds) %>%
  mutate(Retention.Time = as.numeric(as.character(Retention.Time))) %>%
  mutate(RTFlag = ifelse((abs(Retention.Time - RT_ref) > RTflex), "RTFlag", NA))

#Next do Blank flag compared to blank
Area_of_Blanks <- Datorig %>%
  filter(Replicate.Name %in% BlankMatcher$Blank.Name) %>%
  rename(Blank.Name = Replicate.Name,
         Blank.Area = Area) %>%
  select(Blank.Name, Precursor.Ion.Name, Blank.Area) %>%
  left_join(BlankMatcher) %>% select(-Blank.Name)

Dat3 <- Dat2 %>%
  left_join(Area_of_Blanks) %>%
  mutate(BlankFlag = ifelse(Area/Blank.Area < BlankRatiomax, "BlankFlag", NA))

#Finally, combine all the flags and throw out any peak with a flag
Dat4 <- Dat3 %>%
  mutate(Flags = paste(SNFlag, ppmFlag, areaminFlag, RTFlag, BlankFlag, sep = ", ")) %>%
  mutate(Flags = as.character(Flags %>% str_remove_all("NA, ") %>%  str_remove_all("NA"))) %>%
  mutate(QC_area = ifelse(str_detect(Flags, "Flag"), NA, Area))


write.csv(Dat4, "QCoutput.csv")


#To inspect
Dat5 <- Dat4 %>%
  select(Precursor.Ion.Name, Replicate.Name, Flags, QC_area)
  
  
```

## Output with: comment -------------------------
## Ion name, area, was a peak removed?
comment.text <- paste("# Hello! welcome to your data! ","Overload height: ", 
                      max.height, ". ", "RT flexibility: ", RT.flex, ". ",
                      "Blank can be this fraction of a sample: ",blk.thresh, ". ", 
                      "S/N threshold: " , SN.thresh, ". ",
                      "Minimum peak height: ", min.height, ". ",
                      "Processed on: ", Sys.time(), sep="")
new.filename <- paste("QEQC_output",filename,sep="")
con <- file(new.filename, open="wt")
writeLines(paste(comment.text), con)
write.csv(final.output, con)
close(con)

